Coherent optical association of single molecules

### 2020-09-18 paper.tex
WIP: result analysis

% Parameters: Light shift, Rabi frequency, atomic scattering rate, molecular scattering rate
% Variables: detuning, power
% Changes: background, single line

The molecule lifetime measured in the experiment is $...$ larger than the expected value of $...$ calculated from ..... By measuring the lifetime for different tweezer powers, we observed a linear dependency of the lifetime (fig ...). This confirms that the short lifetime is mainly caused by scattering from the tweezer light rather than the intrinsic lifetime of the molecule itself. Additionally, we also measured the loss rate as a function of the tweezer frequency (fig ...) which shows only a very weak dependency for a $...x$ change in the detuning from the $v=0$ excited state. This result is significantly different from the $1/\delta^2$ dependency expected from off-resonant scattering and suggests that the main source of the scattering is due to a broadband process that is not directly related to the $v=0$ excited state. (ASE filter?)

>>>>

Next, we look at the atomic loss rate during the transfer process.
The atomic loss rate scales as the tweezer intensity to the 2.58th power but shows little to no dependency on the tweezer frequency. The lack of frequency dependency suggests that most of the atomic loss are due to the coupling to states other than the $v=0$ one. After substracing 0.58 from the power scaling due to the change in the up leg matrix element, the loss rate is proportional to the tweezer power squared. This is an evidence that the loss is likely caused by a two photon scattering process rather than one photon scattering. The strong power scaling causes a faster than expected loss rate for the atom. However, the atomic scattering is contribution only a small fraction of the total scattering rate so this is not the limiting factor for the transfer.

Finally, we fit the scaling for the molecular loss rate. We observed a dependency on the detuning that is consistent with $1/\delta^2$ suggesting that the loss is indeed mostly coming from the $v=0$ excited state. (preliminary) We observed a power scaling power of $\approx1.2$ which is closed to the prediction for a single photon scattering process. The excited state line width calculated from the scattering rate is $...(1 GHz?)$ which is much larger than the theory prediction of $10 MHz$ as well as the $20 MHz$ upper bound from our previous PA measurements (cite).

(ASE filter)
